### 2015-07-05 narrative/naming-service.tex
fixed some errors

Our research in this area will address the following questions:\\
Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?\\
For POSIX API requests, how do we respond if only varying data fidelity levels
  are available for the requested data object?\\
What level of metadata should we maintain and keep in sync to enhance response
  quality within time-bound requests?\\
How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?\\
How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?\\
% Which data block and what quality/type do we respond to a query with?;\\
% How will we scale a fully distributed storage system's metadata management;\\
% Can we accelerate the discovery process with the addition of an
%    application/user level metadata store that tracks where data was
%    originally written and how was it structured?;\\
% Can we provide time estimates for read/write calls in the presence of
%    an unbounded discovery system? If not how do we bound the discovery time?
% How do we amortize the time cost of discovery vs time cost of actually
%    reading the data (latency vs bandwidth essentially)?

>>>>

Our research in this area will address the following questions:
(1) Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?
(2) For POSIX API requests, how do we respond if only varying data fidelity levels
  are available for the requested data object?
(3) What level of metadata should we maintain and keep in sync to enhance response
  quality within time-bound requests?
(4) How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?
(5) How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?
% Which data block and what quality/type do we respond to a query with?;\\
% How will we scale a fully distributed storage system's metadata management;\\
% Can we accelerate the discovery process with the addition of an
%    application/user level metadata store that tracks where data was
%    originally written and how was it structured?;\\
% Can we provide time estimates for read/write calls in the presence of
%    an unbounded discovery system? If not how do we bound the discovery time?
% How do we amortize the time cost of discovery vs time cost of actually
%    reading the data (latency vs bandwidth essentially)?
